### 2021-07-22 paper/paper.tex
finish first draft of main design choices

@@

Since functions are first-class citizens in Julia, they can be passed around
and used efficiently. Thus, everything that acts like a function can be used
in \trixi, \eg, to define initial/boundary conditions. While such a flexibility
is not too uncommon, two-point numerical fluxes are also just functions with a
specified signature. Thus, users can write their own numerical fluxes in their
own code and they will work and be as efficient as if they were implemented
directly in \trixi.

@@

Abstractions such as the \lstinline{mesh} and the \lstinline{equations} are
based on a common interface. Using multiple dispatch in Julia,

@@

Instead of providing only the very basic discretization ingredients such as
other open source frameworks for PDEs, \trixi includes also some widely used
physical parts to make it easier to use.

\subsubsection{Adding new functionality does not require changing existing code}

@@

@@

@@

@@

\todo{TODO} %TODO
\begin{itemize}
  \item Packages can really be used together at low (or no) cost
  \item Reproducibility
  \item Good software development practices (CI, tests, version management)
  \item Relatively easy to integrate existing C libraries (p4est, HDF5)
  \item more nice features
  \item Can be extended: Multi-physics with 350 lines of code
  \item Compilation time can be annoying but also allows cool features and performance \cite{schlottkelakemper2021purely}
  \item MPI: To be evaluated but the basic tools are already there \cite{byrne2021mpi}
\end{itemize}

>>>>

\todo{TODO %TODO
\begin{itemize}
  \item Why we created \trixi
  \item Overview of the paper \etc
\end{itemize}}

@@

Since functions are first-class citizens in Julia, they can be passed around
and used efficiently. Thus, everything that acts like a function can be used
in \trixi, \eg, to define initial/boundary conditions. While such a flexibility
is not too uncommon, two-point numerical fluxes are also just functions with a
specified signature. Thus, users can implement numerical fluxes in their
own code and they will work and be as efficient as if they were implemented
directly in \trixi.

@@

Abstractions such as (variants of) the \lstinline{solver}, the \lstinline{mesh},
and the \lstinline{equations} are based on a common interface. Using multiple
dispatch in Julia, internal implementations are specialized accordingly. For
example, changing the volume terms of the DG discretization from the standard
weak form to entropy stable and/or shock capturing methods can be achieved by
passing one additional parameter to the \lstinline{DGSEM} constructor in the
example above.

@@

Instead of providing only the very basic discretization ingredients such as
other open source frameworks for PDEs, \trixi includes also some widely used
physical parts to make it easier to use. Nevertheless, users are not restricted
to the physics models bundled in \trixi. To setup a new type of \lstinline{equations},
it is only necessary to create an appropriate \lstinline{struct} bundling all
parameters and implementing pointwise operations such as the calculation of
the fluxes $f^j$ in \eqref{eq:hcl} or two-point numerical fluxes. Due to Julia's
design and just-ahead-of-time compiler, these fluxes can be inlined into the
library functions of \trixi. Thus, the physics can be separated completely from
the \lstinline{solver} but are still very efficient.

@@

In traditional monolithic code bases, it is often necessary to implement a new
feature for all combinations of possible (compile time) options. This effort
can make it hard to experiment with new ideas. In contrast, Julia's dynamic
nature and just-ahead-of-time compiler allow us to implement only the features
that are strictly necessary. For example, if a user wants to simulate a new
physics model only on Cartesian grids with smooth solutions, there is no need
to implement anything for curvilinear coordinates or shock capturing approaches.

@@

\subsection{Description of the setup}

@@

\subsection{Results of the performance comparison}

@@

\todo{TODO %TODO
\begin{itemize}
  \item Packages can really be used together at low (or no) cost
  \item Reproducibility
  \item Good software development practices (CI, tests, version management)
  \item Relatively easy to integrate existing C libraries (p4est, HDF5)
  \item more nice features
  \item Can be extended: Multi-physics with 350 lines of code
  \item Compilation time can be annoying but also allows cool features and performance \cite{schlottkelakemper2021purely}
  \item MPI: To be evaluated but the basic tools are already there \cite{byrne2021mpi}
\end{itemize}}
